{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2024-12-23 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

        Our results are based the assumption $F = f + g$ where $g:Q \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 

@@

        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate. 
        And when $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}, which is an optimal algorithm for a strongly convex $F$. 
        R-WAPG gives the convergence claim, and it's consistent with the literatures. 

@@

        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 

@@

        T_Ly &= \argmin_x \left\lbrace

@@

        The equality is trivially true when $x \in \RR \setminus \dom g$. 

@@

    \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\;\\

>>>>

        Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 

@@

        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
        In Theorem \ref{thm:fixed-momentum-fista}, it demonsrate that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex. 

@@

        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 

@@

        T_Ly &= \argmin_{x \in \RR^n} \left\lbrace

@@

        The equality is trivially true when $x \in \RR^n \setminus \dom g$. 

@@

    \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\

### 2024-12-23 Notebook LaTEX/Proposal/main.tex
>w<, changes

            \begin{lemma}[Proximal gradient model function]\;\\
                Take $\widetilde{\mathcal M}^{L^{-1}}, \mathcal M^{L^{-1}}$ as defined in this section, we will have for all $x \in \RR^n$ that: 
                \begin{align*}
                    \widetilde{\mathcal M}^{L^{-1}}(x; y)
                    &= 
                    \mathcal M^{L^{-1}}(x; y)- D_f(x, y).
                \end{align*}
            \end{lemma}
            \begin{lemma}[A favorable property of gradient mapping]
                Take $F:= f + g$ as defined in this section. 
                Fix any $x \in \RR^n$. 
                Then there exists $v \in \partial g(T_L x)$ such that $\mathcal G_L (x) = v + \nabla f(x)$. 
            \end{lemma}
            \begin{remark}
                This lemma still holds for non-convex $f$. 
            \end{remark}
            \begin{lemma}[The proximal gradient inequality]
                Take $F:= f + g$ as defined in this section. 
                Fix any $y \in \RR^n$, then for all $x$, the proximal gradient inequality is true: 
                \begin{align*}
                    (\forall x \in \RR^n)\quad 
                    h(x)  - h(Ty) - \langle L(y - Ty), x - y\rangle
                    - \frac{\mu}{2}\Vert x - y\Vert^2 - \frac{L}{2}\Vert y - Ty\Vert^2 
                    &\ge 0. 
                \end{align*}
            \end{lemma}
            \begin{remark}
                This lemma is proved in our draft paper. 
            \end{remark}

@@

            \item Method of Nesterov's estimating sequence.

@@

    All theorems and claims stated in this section have proofs. 

@@

    \subsection{Our Contributions}

\section{Method Free R-WAPG}\label{sec:spectral-momentum}
    \todoinline{
        Algorithm, and results of numerical experiments with their descriptions. 
    }
\section{Catalyst accelerations and future works}\label{sec:catalyst}
    \todoinline{\noindent
        Literatures review of the topics in Catalyst acceleration method. 
        Here is a list of topics: 
        \begin{enumerate}
            \item The original accelerated PPM. 
            \item The Catalyst with weakly convex objectives. 
        \end{enumerate}
        After the literature reviews of the core literatures, move on and state new research directions and open problems. 
        There are several directions for open problem: 
        \begin{enumerate}
            \item APPM method for monotone operators instead of just subgradient, whether the same framework exists in a greater context. 
            \item Accelerated Proximal Bregman Method. 
        \end{enumerate}  
    }
    \todoinline{\noindent
        A list of relevant literatures: 
        \begin{enumerate}
            \item Güler's 1992 paper on Accelerated Proximal Point method. 
            \item Lin's, and Payquette's three triology paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
        \end{enumerate}
    }

>>>>

            \begin{lemma}[Proximal gradient model function]\;\\
                Take $\widetilde{\mathcal M}^{L^{-1}}, \mathcal M^{L^{-1}}$ as defined in this section, we will have for all $x \in \RR^n$ that: 
                \begin{align*}
                    \widetilde{\mathcal M}^{L^{-1}}(x; y)
                    &= 
                    \mathcal M^{L^{-1}}(x; y)- D_f(x, y).
                \end{align*}
            \end{lemma}
            \begin{lemma}[A favorable property of gradient mapping]
                Take $F:= f + g$ as defined in this section. 
                Fix any $x \in \RR^n$. 
                Then there exists $v \in \partial g(T_L x)$ such that $\mathcal G_L (x) = v + \nabla f(x)$. 
            \end{lemma}
            \begin{remark}
                This lemma still holds for non-convex $f$. 
            \end{remark}
            \begin{lemma}[The proximal gradient inequality]\label{thm:prox-grad-ineq}
                Take $F:= f + g$ as defined in this section. 
                Fix any $y \in \RR^n$, then for all $x$, the proximal gradient inequality is true: 
                \begin{align*}
                    (\forall x \in \RR^n)\quad 
                    h(x)  - h(Ty) - \langle L(y - Ty), x - y\rangle
                    - \frac{\mu}{2}\Vert x - y\Vert^2 - \frac{L}{2}\Vert y - Ty\Vert^2 
                    &\ge 0. 
                \end{align*}
            \end{lemma}
            \begin{remark}
                This lemma is proved in our draft paper. 
            \end{remark}

@@

            \item \st{Method of Nesterov's estimating sequence.}
            \item R-WAPG stepwise definition 
            \item R-WAPG stepwise convergence claim

@@

    All theorems and claims stated in this section have proofs in the draft paper. 

@@

    \subsection{Our Contributions, organizations}
        Our contributions are two folds, theoretical and practical. 
        Our results are based the assumption $F = f + g$ where $g:R^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:nag_example} and showed an upper bound of the optimal gap. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
        \begin{align*}
            \mathcal O\left(
                \left(
                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
                \right)
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right). 
        \end{align*}
        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
        In Theorem \ref{thm:fixed-momentum-fista}, it demonsrate that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex. 
        \par
        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
        \par
        Organization now follows. 
        \todoinline{Finish the organizations here after this section is finished. }
    \subsection{Building Blocks of R-WAPG}

    \subsection{R-WAPG Sequence and R-WAPG algorithm}

    \subsection{Equivalent forms of R-WAPG algorithm}

    \subsection{The descriptive power of R-WAPG on existing variants}

\section{Method Free R-WAPG}\label{sec:spectral-momentum}
    \todoinline{
        Algorithm, and results of numerical experiments with their descriptions. 
    }

\section{Catalyst accelerations and future works}\label{sec:catalyst}
    \todoinline{\noindent
        Literatures review of the topics in Catalyst acceleration method. 
        Here is a list of topics: 
        \begin{enumerate}
            \item The original accelerated PPM. 
            \item The Catalyst with weakly convex objectives. 
        \end{enumerate}
        After the literature reviews of the core literatures, move on and state new research directions and open problems. 
        There are several directions for open problem: 
        \begin{enumerate}
            \item APPM method for monotone operators instead of just subgradient, whether the same framework exists in a greater context. 
            \item Accelerated Proximal Bregman Method. 
        \end{enumerate}  
    }
    \todoinline{\noindent
        A list of relevant literatures: 
        \begin{enumerate}
            \item Güler's 1992 paper on Accelerated Proximal Point method. 
            \item Lin's, and Payquette's three triology paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
        \end{enumerate}
    }
